---
title: "cran-comments"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Package built by

```{r eval = FALSE}
library("devtools")
build()
```

## R CMD check results

Status OK

There was no ERROR, WARNING or NOTE.


## Downstream dependencies

I have run 

```{r eval=FALSE}
revdep_check()
```

There was 1 reverse dependency, `brokenstick`. The check on this package did not run.

# Platform

|field    |value                                                                                               |
|:--------|:---------------------------------------------------------------------------------------------------|
|version  |R version 4.4.0 (2024-04-24)                                                                        |
|os       |macOS Sonoma 14.4.1                                                                                 |
|system   |aarch64, darwin20                                                                                   |
|ui       |RStudio                                                                                             |
|language |(EN)                                                                                                |
|collate  |en_US.UTF-8                                                                                         |
|ctype    |en_US.UTF-8                                                                                         |
|tz       |Europe/Amsterdam                                                                                    |
|date     |2024-05-03                                                                                          |
|rstudio  |2024.04.0+735 Chocolate Cosmos (desktop)                                                            |
|pandoc   |3.1.11 @ /Applications/RStudio.app/Contents/Resources/app/quarto/bin/tools/aarch64/ (via rmarkdown) |

# Dependencies

|package     |old    |new    |Δ  |
|:-----------|:------|:------|:--|
|AGD         |0.39   |NA     |*  |
|gamlss      |5.4-22 |5.4-22 |   |
|gamlss.data |6.0-6  |6.0-6  |   |
|gamlss.dist |6.1-1  |6.1-1  |   |

# Revdeps

## New problems (1)

|package     |version |error |warning |note   |
|:-----------|:-------|:-----|:-------|:------|
|[brokenstick](problems.md#brokenstick)|2.5.0   |      |        |__+1__ |

# brokenstick

<details>

* Version: 2.5.0
* GitHub: https://github.com/growthcharts/brokenstick
* Source code: https://github.com/cran/brokenstick
* Date/Publication: 2023-03-22 23:00:06 UTC
* Number of recursive dependencies: 119

Run `revdepcheck::revdep_details(, "brokenstick")` for more info

</details>

## Newly broken

*   checking package dependencies ... NOTE
    ```
    Package suggested but not available for checking: ‘AGD’
    ```

